(Working Title) Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Validation of \Nvalidated\ Systems, (Including a Planet Receiving Earth-like Insolation?)

### 2015-03-09 table_fpp.tex
table formatting

 \color{red} $201257461$ \color{black} & \color{red}  $1$ \color{black} & \color{red}  $0.59$ \color{black} & \color{red}  $< 10^{-4}$ \color{black} & \color{red}  $0.072$ \color{black} & \color{red}  $0.93$ \color{black} & \color{red}  $0.22$ \color{black} & \color{red}  $1$\color{black} \\

@@

 \color{red} $201565013$ \color{black} & \color{red}  $1$ \color{black} & \color{red}  $1.69$ \color{black} & \color{red}  $0.0023$ \color{black} & \color{red}  $0.14$ \color{black} & \color{red}  $0.82$ \color{black} & \color{red}  $0.07$ \color{black} & \color{red}  $0.96$\color{black} \\

@@

 \color{red} $201649426$ \color{black} & \color{red}  $1$ \color{black} & \color{red}  $3.10$ \color{black} & \color{red}  $0.81$ \color{black} & \color{red}  $0.0016$ \color{black} & \color{red}  $0.13$ \color{black} & \color{red}  $0.01$ \color{black} & \color{red}  $0.94$\color{black} \\

@@

 \color{red} $201505350$ \color{black} & \color{red}  $1$ \color{black} & \color{red}  $2.69$ \color{black} & \color{red}  $< 10^{-4}$ \color{black} & \color{red}  $0.13$ \color{black} & \color{red}  $0.86$ \color{black} & \color{red}  $0.18$ \color{black} & \color{red}  $0.99$\color{black} \\
$201754305$ & $1$ & $0.65$ & $< 10^{-4}$ & $0.015$ & $0.0016$ & $0.18$ & $0.017$ \\

>>>>

 \cellcolor{red} $201257461$  & \cellcolor{red}  $1$  & \cellcolor{red}  $0.59$  & \cellcolor{red}  $< 10^{-4}$  & \cellcolor{red}  $0.072$  & \cellcolor{red}  $0.93$  & \cellcolor{red}  $0.22$  & \cellcolor{red}  $1$\\

@@

 \cellcolor{red} $201565013$  & \cellcolor{red}  $1$  & \cellcolor{red}  $1.69$  & \cellcolor{red}  $0.0023$  & \cellcolor{red}  $0.14$  & \cellcolor{red}  $0.82$  & \cellcolor{red}  $0.07$  & \cellcolor{red}  $0.96$\\

@@

 \cellcolor{red} $201649426$  & \cellcolor{red}  $1$  & \cellcolor{red}  $3.10$  & \cellcolor{red}  $0.81$  & \cellcolor{red}  $0.0016$  & \cellcolor{red}  $0.13$  & \cellcolor{red}  $0.01$  & \cellcolor{red}  $0.94$\\

@@

 \cellcolor{red} $201505350$  & \cellcolor{red}  $1$  & \cellcolor{red}  $2.69$  & \cellcolor{red}  $< 10^{-4}$  & \cellcolor{red}  $0.13$  & \cellcolor{red}  $0.86$  & \cellcolor{red}  $0.18$  & \cellcolor{red}  $0.99$\\
$201754305$ & $1$ & $0.65$ & $< 10^{-4}$ & $0.015$ & $0.0016$ & $0.18$ & $0.017$
